How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-11 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

The ANZCTR was established in 2005 as part of a coordinated global effort to improve research quality and transparency in clinical trials reporting. Researchers responsible for overseeing a clinical trial are expected to register full details before commencing participant enrolment. Details required for registration follow a standardised template (reference or supp file), which covers important details about participant eligibility, intervention(s) being evaluated, study design and outcomes. As part of study design, researchers are required to provide a "brief description" of the sample size calculations, statistical methods and planned analyses [@ANZCTR]. 
<!---Upon successful registration, the trial is assigned a unique registration number for use in future reporting in scientific publications. --->
All trials registered on ANZCTR are publicly available and can be searched for via an online portal.

All studies available on ANZCTR were downloaded on 1 February 2020 in XML format. Studies were excluded if the statistical methods section was empty or labelled as "Not applicable", "Nil" or "None".

@@

@@

There were 28,008 downloaded studies, and 9,632 (34\%) had a statistical methods section.
Of the 12,700 eligible applications, 9523 (75%) had a statistic section

@@

>>>>

The ANZCTR was established in 2005 as part of a coordinated global effort to improve research quality and transparency in clinical trials reporting. All trials registered on ANZCTR are publicly available and can be searched for via an online portal. Researchers responsible for overseeing a clinical trial are expected to register full details before commencing participant enrolment. Details required for registration follow a standardised template (reference or supp file), which covers important details about participant eligibility, intervention(s) being evaluated, study design and outcomes. Researchers are asked to provide a "brief description" of the sample size calculations, statistical methods and planned analyses, but this section is not compulsory [@ANZCTR]. 
<!---Upon successful registration, the trial is assigned a unique registration number for use in future reporting in scientific publications. --->

All studies available on ANZCTR were downloaded on 1 February 2020 in XML format. 
Studies prior to 2013 were excluded as the statistical methods section appeared to be introduced in 2013.

@@

## Missing statistical methods sections

The statistical methods section for the ANZCTR data was somtimes missing and so we examined if there were particular studies where this section was more likely to be missing. 
We used a logistic regression model fitted using a Bayesian paradigm. A small number of sections were labelled as "Not applicable", "Nil" or "None" and we changed these to missing.

@@

There were 28,008 downloaded studies, and 9,632 (34%) had a statistical methods section. 
The numbers of excluded studies are shown in Figure~X. 
Of the 12,700 eligible applications, 9523 (75%) had a statistic section.

The odds ratios and 95% credible intervals are shown in Table~X.

@@

Some of the sections were only one word, including "ANOVA", "t-test", "SPSS" and even "SSPS". The median length of the section was 129 words with an inter-quartile range of 71 to 219 words.
